\songtitle{Sörkan Sällit}{Polyteknikkojen Kuoro}{2015}
\medskip

\columnratio{0.48}
\begin{paracol}{2}
\small

\begin{guitar}
	\songsection{Verse 1}
	Sörnai gusha nietu molotova,
	sörnai gusha herba moskova,
	\ltrepeat Njet, njet bonimai votvot risubuska,
	dara zeva votvot harashoo. \rtrepeat

	\songsection{Verse 2}
	Isä Stalin, äiti Hrushtsheva
	isgi silmää ginihibragas’,
	\ltrepeat Oi, oi oisiba vodkaa ollut heillä
	oisi isgu gäynyd alemmas. \rtrepeat

	\songsection{Verse 3}
	Tuoksuu tuomet, syreenit ja ruusut,
	tuoksuu tuolla Volgan randamill’,
	\ltrepeat Ai, ai, kaunis kulta Kaditzusha
	tuoksuu tunteet rindas rindamil. \rtrepeat

	\songsection{Verse 4}
	Siellä missä versoaapi vilja,
	siellä kasvoi kaunis Katjuska.
	\ltrepeat Katjuskalla komiat on keuhkot,
	basga haisee Nevan rannalla. \rtrepeat

	\songsection{Verse 5}
	Oon vain köyhä kolhoosinainen,
	ei oo mulla yhtään ystävää.
	\ltrepeat Ei ole lehmää eikä ole lammasta
	eikä suussa yhtään hammasta. \rtrepeat

	\songsection{Verse 6}
	Siperian lakeus on suuri,
	Sonja siellä lunta lapioi.
	\ltrepeat Sonjalla kävi hiton huono tuuri kun
	länsituuli uutta lunta toi. \rtrepeat

	\songsection{Verse 7}
	Olen köyhä poika Petroskoista,
	ei oo mulla yhtään ystävää.
	\ltrepeat Sirppi ja vasara ne taivahalla loistaa,
	basga haisee, balalaikka soi! \rtrepeat
\end{guitar}

\switchcolumn

\begin{guitar}
	\songsection{Translation: Verse 1}
	Sörnai gusha nietu molotova,
	sörnai gusha herba moskova,
	Njet, njet bonimai votvot risubuska,
	dara zeva votvot harashoo.

	\songsection{Translation: Verse 2}
	Father Stalin, mother Hrushtsheva
	winked their eyes, drunk because of gin
	Oh, oh, if only they would've had vodka
	it would have struck a bit lower

	\songsection{Translation: Verse 3}
	Bird cherries, lilacs and roses smell
	they smell there on the shores of river Volga
	Ah, ah, beautiful darling Kaditzusha
	emotions smel on the front of your breasts

	\songsection{Translation: Verse 4}
	Where the grain is growing
	grew the beautiful Katjuska.
	Katjuska has gorgeous lungs,
	shit stinks on the shores of river Neva

	\songsection{Translation: Verse 5}
	I am only a poor woman from a kolkhoz
	I don't have any friends.
	I don't have a cow or a sheep
	nor do I have a single teeth in my mouth

	\songsection{Translation: Verse 6}
	Siberian plain is enormous
	Sonja is shoveling snow there
	Sonja had rotten luck when
	west wind brought new snow

	\songsection{Translation: Verse 7}
	I am a poor boy from Petrozavodsk
	I don't have any friends
	Sickle and hammer shine in the sky
	shit stinks, balalaika plays!
\end{guitar}
\end{paracol}
